### 2019-07-12 papers/journal/intro.tex
Minor fix

In contrast, here we seek to understand the properties of vesicle traffic networks
over all possible update rules, not just for a sampled subset.
%
Formal verification tools like model checkers, SAT (Boolean satisfiability), SMT (satisfiability modulo theories) and QBF (quantified Boolean formula) solvers serve precisely this purpose. 
%
%Formal verification tools, such as model checkers
%\cite{clarke1996symbolic, biere2003bounded, clarke2008birth,
%	cimatti2000nusmv, holzmann1997model} and SAT solvers
%\cite{moskewicz2001chaff,een2004extensible} serve precisely this
%purpose.
%%
The tools model the computation symbolically for the graphs of finite size and can predict the hypothesis for all possible states of the system without explicit enumeration of rules. 
%
In recent work \cite{shukla2017discovering}, we employed the model checker CBMC \cite{ckl2004} meant to analyze ANSI C programs for studying this problem. 
%
VTSs and SNARE regulations were modeled as C code using arrays to represent graphs and Boolean tables. 
%
The graph connectivity question for different variations of SNARE regulations was modeled as logical assertions to be checked by the model checker. 
%
Although the performance was satisfactory, the encoding was non-optimal and hence scalability of the method was insufficient. The tool was able to handle the system with just eight compartments.
%
Another interesting question of property involving quantifiers (was termed as sufficient condition i
n \cite{shukla2017discovering}; in this paper, we call it universal condition) was partly handled
using sampling and left open.
%
We also worked on the synthesis of the unknown pieces may
be {\em assisted} by computation on the graph model of VTSs~\cite{synthesisGupta}.
%
In the work, we developed encoding for the synthesis problem.
%
This paper brings together the above encodings with extended experiments and more detailed
expositions for the benefit of both biological and computation community.
We additionally explored QBF based encoding of some of the problems.

>>>>

In contrast, here we seek to understand the properties of vesicle traffic networks
over all possible update rules, not just for a sampled subset.
%
Formal verification tools like model checkers, SAT (Boolean satisfiability), SMT (satisfiability modulo theories) and QBF (quantified Boolean formula) solvers serve precisely this purpose. 
%
%Formal verification tools, such as model checkers
%\cite{clarke1996symbolic, biere2003bounded, clarke2008birth,
%	cimatti2000nusmv, holzmann1997model} and SAT solvers
%\cite{moskewicz2001chaff,een2004extensible} serve precisely this
%purpose.
%%
The tools model the computation symbolically for the graphs of finite size and can predict the hypothesis for all possible states of the system without explicit enumeration of rules. 
%
In recent work \cite{shukla2017discovering}, we employed the model checker CBMC \cite{ckl2004} meant to analyze ANSI C programs for studying this problem. 
%
VTSs and SNARE regulations were modeled as C code using arrays to represent graphs and Boolean tables. 
%
The graph connectivity question for different variations of SNARE regulations was modeled as logical assertions to be checked by the model checker. 
%
Although the performance was satisfactory, the encoding was non-optimal and hence scalability of the method was insufficient. The tool was able to handle the system with just eight compartments.
%
Another interesting question of property involving quantifiers (was termed as sufficient condition in \cite{shukla2017discovering}; in this paper, we call it universal condition) was partly handled
using sampling and left open.
%
We also worked on the synthesis of the unknown pieces may
be {\em assisted} by computation on the graph model of VTSs~\cite{synthesisGupta}.
%
In the work, we developed encoding for the synthesis problem.
%
This paper brings together the above encodings with extended experiments and more detailed
expositions for the benefit of both biological and computation community.
We additionally explored QBF based encoding of some of the problems.
